%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Job title
    {Age Partnership} % Organization
    {Leeds, United Kingdom} % Location
    {September 2017 - now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed, maintained, and enhanced a call processing web application, which utilizes .NET, HTMX, RabbitMQ and Azure Active Directory (Azure AD) Authentication that imports audio recordings, transcribes them using OpenAI's Whisper models, and integrates Azure's OpenAI models to facilitate advanced querying and interaction with the transcriptions. }
        \vspace{0.7em} % Adds vertical space between items
         \item {Integrated the client's software with soliciting firms' APIs to enhance data exchange and functionality. }
         \vspace{0.7em} % Adds vertical space between items
        \item {Integrated a renowned bank's payment processing service for seamless client payments using Go and HTMX. }
        \vspace{0.7em} % Adds vertical space between items
        \item {Created the first prototype for a client facing portal using ReactJS. }
        \vspace{0.7em} % Adds vertical space between items
        \item {Integrated Open AI's API to be used throughout the client's business. }
        \item {Integrated Credit Kudos' Open Banking API into Age Partnership's services. }
        \vspace{0.7em} % Adds vertical space between items
        \item {Developed a solution to handle the introduction of potential client leads from Daily Mail Group's (Daily Mail) website. }
        \vspace{0.7em} % Adds vertical space between items
        \item {Maintained and enhanced the Insurance Software using WPF.}
        \vspace{0.7em} % Adds vertical space between items
        \item {Was responsible to maintaining and enhancing their advisor facing Pension, Equity Release and Legal Software using WinForms.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
